---
title: "sketch_intro_ii"
output: html_document
date: "2022-10-18"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(conformr)
library(magrittr)
library(dplyr)
```

# Introduction

-   Define what is the problem the package addresses

-   Describe the two cases the package can handle:

    1.  You have access to Source Data (`df_data_in`) as follows:

    ```{r}



    # Example of data available 
    df_data_in <- dplyr::tribble(~source_code, ~value_in,
                                "x1111", 100,
                                "x2222", 30,
                                "x3333", 20,
                                "x4444", 80,
                                "x5555", 30,
                                "x6666", 40,
                                "x7777", 15
                                )
    df_data_in
    ```

    and also to a concordance between the Source Classification (`source_code`) and the Target Classification ( `target_code`), as shown below:

```{r}
   
df_concordance <- dplyr:: tribble(~source_code, ~ target_code,
                                "x1111", "A1",
                                "x2222", "B2",
                                "x2222", "B3",
                                "x3333", "C5",
                                "x4444", "C5",
                                "x5555", "D6",
                                "x5555", "D7",
                                "x6666", "D6",
                                "x6666", "D7",
                                "x7777", "D6"
                                )
df_concordance
```

Conformr **can** make a valid Panel Map (`df_map`) for you by creating, for each observation, weights between (0, 1] depending on whether the number of distinct Target Codes matched to 1 `source_code` (`n_distinct_tc_in_sc`) is greater than or equal to 1. In fact, if *m* is the number of distinct target codes matched to 1 `source_code`, then the assigned weight is 1/*m,* as shown in the data frame `df_weights` below.

```{r}
df_weights <- left_join(df_data_in, df_concordance, by="source_code")
df_weights <- df_weights %>%
  group_by(source_code) %>%
  mutate(n_distinct_tc_in_sc = n_distinct(target_code))%>%
mutate(weight = 1/n_distinct_tc_in_sc)
df_weights
```

An important conceptual insight that follows from data frame `df_weights` is that mapping the Source Classification into the Target Classification four cases may arise. To see these clearly, consider the number of distinct Source Codes that match to one Target Code (`n_distinct_sc_in_tc`), as well as the the number of distinct Target Codes that match to one Source Code (`n_distinct_tc_in_sc`) as shown below. The One-to-One case arises when one distinct Source Code maps into one distinct Target Code (`n_distinct_sc_in_tc`=`n_distinct_tc_in_sc`=1). The One-to-Many case arises when one distinct Source Code maps into many distinct Target Code (`n_distinct_sc_in_tc`=1 and `n_distinct_tc_in_sc`\>1). The Many-to-One case arises when many distinct Source Codes map into one distinct Target Code (`n_distinct_sc_in_tc`\>1 and `n_distinct_tc_in_sc`=1). The Many-to-Many case arises when many distinct Source Codes map into many distinct Target Code (`n_distinct_sc_in_tc`\>1 and `n_distinct_tc_in_sc`\>1). These mapping cases are typically described in the correlation tables of published concordances and what practitioners often refer to describing concordances. [ADD Sankey Visualization here? ]

```{r}
df_weights <- df_weights %>%
  group_by(target_code) %>%
  mutate(n_distinct_sc_in_tc = n_distinct(source_code))
df_weights[, c(1,3:4,6)]
```

The Panel Map (`df_map`) Conformr provides, in our example, is:

```{r}
df_map <- df_weights[,c(1,3,5)]
df_map
```

Once it is created, Conformr applies it to `df_data_in` to get a `value_out` for each `destination_code`. The underlying process is best described in three steps:

1.  Merge data frames `df_data_in` and `df_map` by `source_code`

```{r}
df_process <-left_join(df_data_in, df_map, by="source_code")
df_process

```

2.  Generate `weighted_value` by multiplying the `weight` by `value_in`

```{r}
df_s2 <- mutate(df_process, weighted_value=weight*value_in)
df_s2
```

3.  Aggregate `weighted_value` by `destination_code` in `value_out`

```{r}
df_output <- df_s2 %>%
  group_by(target_code)%>%
  mutate(value_out=sum(weighted_value))%>%
distinct(target_code, value_out)
df_output
```

Conformr implements a number of checks:

1.  sum of weight by source_code =1
2.  total value_in = total value_out
