---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(conformr)
library(magrittr)
library(dplyr)
```

# Introduction

-   Define what is the problem the package addresses

-   Describe the two cases the package can handle:

    1.  You have access to data as follow:

    ```{r}



    # Example of data available 
    tribble(~Source_Code, ~Value,
                                "x1111", 100,
                                "x2222", 30,
                                "x3333", 20,
                                "x4444", 80,
                                "x5555", 30,
                                "x6666", 40,
                                "x7777", 15
                                )

    ```

    and also to a correspondence between the classification of the Source_code and that of a Destination_code, as shown below:

```{r}
   
tribble(~Source_Code, ~ Destination_Code,
                                "x1111", "A1",
                                "x2222", "B2",
                                "x3333", "B2",
                                "x4444", "C3",
                                "x4444", "C4",
                                "x4444", "C5",
                                "x5555", "D6",
                                "x5555", "D7",
                                "x6666", "D6",
                                "x6666", "D7",
                                "x7777", "D6"
                                )

```

Conformr makes a valid panel map for you by creating weights between (0, 1] depending on whether 1 code in the Source_Code classification matches to one or more codes in the Destination_code classification. In the 1-1 case the assigned weight is 1. In the case in which 1 code in the Source_code classification matches to m codes in the Destination_Code classification, the assigned weight is 1/m.

```{r}
   
tribble(~Source_Code, ~ Destination_Code, ~Weight,
                                "x1111", "A1", 1,
                                "x2222", "B2", 1,
                                "x3333", "B2", 1,
                                "x4444", "C3", 1/3,
                                "x4444", "C4", 1/3,
                                "x4444", "C5", 1/3,
                                "x5555", "D6", 1/2,
                                "x5555", "D7", 1/2,
                                "x6666", "D6", 1/2,
                                "x6666", "D7", 1/2,
                                "x7777", "D6", 1/2
                                )

```
